The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-05-12 paper.tex
Played around with bib file to remove doi but to no avail.
Added abstract

\begin{abstract}
%%%
Please Type your abstract here. Type your abstract here. Type your abstract
here. Type your abstract here. Type your abstract here. Type your
abstract here. Type your abstract here. Type your abstract here. Type
your abstract here. Type your abstract here. Type your abstract here.
Type your abstract here. Type your abstract here.Type your abstract here. 
Type your abstract here. Type your abstract here. Type your abstract here. 
Type your abstract here. Type your abstract here. Type your abstract here.

Please Type your abstract here. Type your abstract here. Type your abstract
Please Type your abstract here. Type your abstract here. Type your abstract
here. Type your abstract here. Type your abstract here. Type your
abstract here. Type your abstract here. Type your abstract here. Type
your abstract here. Type your abstract here. Type your abstract here.
Type your abstract here. Type your abstract here.
Please Type your abstract here. Type your abstract here. 
Type your abstract here.
%%%%
\end{abstract}

@@

We begin in Section \ref{sec:math} with an overview of the mathematical treatment of linear optical transformation on single photons, and in Section \ref{sec:encoding} with a description of some commonly used qubit encodings. Any unitary transformation acting on the spatial label of single photons can be efficiently decomposed into a network of beamsplitters and phase-shifters. We discuss this, and an analogous decomposition for single photons with additional internal states, in Section \ref{sec:decomp}. For applying any linear optical circuit, one needs an accurate description of its unitary representation. A full quantum tomography is costly and time-consuming. Some practical methods have been devised to do this reconstruction without resorting to tomography, and these are described in Section \ref{sec:reconstruction}.

@@

\section*{References}

>>>>

\begin{abstract}
%%%
Linear optics has seen a resurgence owing to its miniaturisation on-chip, and increase in production efficiency and quality of single photons. Time-bin encodings have also become feasible owing to fresh architecture, and processing capabilities. Theoretical efforts to find useful application beyond a full universal quantum computation has also bore fruit. A sampling task, known as {\sc bosonsampling} that is easily implemented using linear optics but is strongly believed to be a hard for a classical computer, has emerged. 
%%%%
\end{abstract}

@@

We begin in Section \ref{sec:math} with an overview of the mathematical treatment of linear optical transformation on single photons, and in Section \ref{sec:encoding} with a description of some commonly used qubit encodings. Any unitary transformation acting on the spatial label of single photons can be efficiently decomposed into a network of beamsplitters and phase-shifters. We discuss this, and an extension to handle additional internal states, in Section \ref{sec:decomp}. For applying any linear optical circuit, one needs an accurate description of its unitary representation. A full quantum tomography is costly and time-consuming. Some practical methods have been devised to do this reconstruction without resorting to tomography, and these are described in Section \ref{sec:reconstruction}.

@@
